Matching bullets

### 2015-11-21 imaging-paper.Rnw
number of consecutive matches

# smooth
lofX <- lofX %>% group_by(bullet) %>% mutate(
  l30 = smoothloess(y, resid, span = 0.03)
)
# cut at .75
lofX$r05 <- 0.75* sign(lofX$l30) * as.numeric(abs(lofX$l30) > .75)
lofX$type <- factor(lofX$r05)
levels(lofX$type) <- c("groove", NA, "peak")
@

@@

>>>>

# smooth
lofX <- lofX %>% group_by(bullet) %>% mutate(
  l30 = smoothloess(y, resid, span = 0.03)
)

# cut at .75
threshold <- .75
lofX$r05 <- threshold* sign(lofX$l30) * as.numeric(abs(lofX$l30) > threshold)
lofX$type <- factor(lofX$r05)
levels(lofX$type) <- c("groove", NA, "peak")
@

@@

\hh{XXX what would be good is to get the line identifications and project them back onto the surface. }
